\documentclass[10pt,a4paper]{article}

\usepackage[cm]{fullpage}
\usepackage[usenames,svgnames]{xcolor}
\usepackage{enumitem}
\setlist[itemize]{format=\textbf, leftmargin=2.5cm}

\title{\underline{A Pantomime} \\ \small Prompt Script: Hero X}
\author{David Sanders}

% -- Define environments and commands --
% Define scenetitle and note commands
\newcommand{\scenetitle}[1]{{\Large{\textsc{#1}}}}
\newcommand{\note}[1]{\textit{#1}}
% Define scene flow environment
\newenvironment{sceneflow}{\begin{enumerate}[label=\roman*., leftmargin=0em]}{\end{enumerate}}
% Define song command
\newcounter{song}
\newcommand{\song}[0]{\refstepcounter{song}SONG~\thesong:}
% Define prompt commands: \voc - sing/speak, \act - act!
\newcommand{\voc}[1]{{\large{\color{Green}#1}}}
\newcommand{\act}[1]{{\large{\color{Red}\textit{*#1*}}}}

\begin{document}
\maketitle

\begin{enumerate}
% Act 1
% \input{./1-0.tex}
\item [1-0:] \scenetitle{Prologue}
\begin{sceneflow}
\item \note{The Sorcerer declares his villainous intent.}
\item \note{The Sorcerer heads off to devise dastardly deeds.}
\end{sceneflow}
% \input{./1-1.tex}
\item [1-1:] \scenetitle{Location A}
\begin{sceneflow}
\item \note{The Heroes enter.}
\begin{itemize}
\item [A] X is missing!
\item [\song] \textbf{Where is X?} \\
It seems to be fate \\
That on this date \\
Though he is great \\
X is late \\
Has anybody... \\
Seen our mate?
\end{itemize}
\item \note{X appears towards the back of the stage, looking dishevelled.}
\begin{itemize}
\item [Z] How much did you drink last night?!
\end{itemize}
\end{sceneflow}
% \input{./1-2.tex}
\item [1-2:] \scenetitle{Location B}
\begin{sceneflow}
\item \note{Something happens.}
\item \note{Heroes X and Y enter.}
\begin{itemize}
\item [\song] \textbf{X\&Y's Duet} \\
\voc{
X Line 1 \\
X Line 2 \\
X Line 3 \\
X Line 4 }

\medskip
Y Line 1 \\
Y Line 2 \\
Y Line 3 \\
Y Line 4

\medskip
\voc{
X\&Y Line 1 \\
X\&Y Line 2 }
\item [Y] ... bla bla blah.
\item [X] \voc{Well, bla lah dah blah var zah maa.}
\item [Z] ...
\item [A] ...
\item [Y] ... woffle poffle toffle!
\item [X] \voc{Wha boo ya Z - gada nada fada zada - or zoor loor moor door!}
\item [X\&Y] \act{Guffaw}
\item [Y] ... Zoop wobity blobity!
\item [X] \voc{I'm sorry but I didn't understand any of that!}
\end{itemize}
\item \note{The Heroes take a reality check and suddenly realise the Sorcerer is amongst them.}
\begin{itemize}
\item [HEROES] \act{Look towards the Sorcerer}
\item [Y] Wooooah! Where the hell did he come from?!
\item [Sorcerer] ... soon you will all bow to me!
\item [X] \voc{That's what you think! I, Character X, bow to no one!}
\item [A] ...
\item [Z] ...
\item [Sorcerer] You peasants! BE SILENT!
\item [HEROES] \act{Struck dumb - draw swords and slap thighs}
\item [Sorcerer] What? Are you trying to scream for your mummies? MWHAHAHA!
\item [HEROES] \act{Prepare to charge}
\item [Sorcerer] DISARMUS!
\item [HEROES] \act{Drop swords, charge with fists brandished}
\item [Sorcerer] GET STONED!
\item [HEROES] \act{Freeze}
\item [Sorcerer] ...
\end{itemize}
\item \note{B emerges from hiding and rushes off to find help or a decent writer.}
\end{sceneflow}

% Act 2
% \input{./2-1.tex}
% \input{./2-2.tex}
\end{enumerate}

\end{document}
